---
title: "An Knitr Example Using Warpbreaks Data"
author: "Justin Meyer"
date: "February 17, 2015"
output: pdf_document
---

To make a knitr file go to File then New File then R Markdown...

RStudio will ask you to install some necessary packages.

RStudio can turn this code into an HTML file, a PDF, or a Word doc.
A PDF requires that you have TeX installed. MikTex is recommended for Windows.
A Word doc requires that you have Word installed.

The above text will show up in the output document just as it appears here.

You can use Markdown to add formatting to the text. There is example markdown at
[http://daringfireball.net/projects/markdown/syntax](http://daringfireball.net/projects/markdown/syntax).

Here are some bullets:  
- Note 1  
- Note 2

We can also add a pagebreak. Note that pagebreak is done with LaTeX.
Some LaTeX works and some doesn't.

\pagebreak

# This Page has an H1 Header

The following is some R code that will run. echo = FALSE hides the R code so only
the output is shown

### Here is the Table

```{r, echo = FALSE}

# Everything inside ```{r} is R code. Everything that is outside is Markdown.

###############################
# Set some global options for R
###############################

# Sometimes you might want to set global R options to hide warning messages
# You can do this with
# options(warn=-1)

# There are other options like
# options(width = 100)

##############################################
# Make a table summarizing the warpbreaks data
##############################################

# Get data
data(warpbreaks)

# Load the data.table package
library(data.table)

# Create an object that data.table can use
temp <- data.table(warpbreaks)

# Aggregate using data.table
results <- as.data.frame(temp[, list(
  average_breaks = mean(breaks),
  samples = length(breaks)),
  by = list(wool, tension)])
rm(temp)

# Change the names of the fields in the table so they look good
setnames(results, old = c("wool", "tension", "average_breaks", "samples"), 
         new = c("Wool", "Tension", "Average Breaks", "Number of Samples"))

# Print the table
# row.names = FALSE hides the table row names
library(knitr)
kable(results, row.names = FALSE)

```

\newpage

# A Chart Summarizing the Warpbreaks Data

```{r, echo = FALSE}

# Make a boxplot
boxplot(breaks ~ tension, data = warpbreaks, main = "Warpbreaks Data", 
    xlab = "Tension", ylab = "Breaks")

```

Add inline R code like this:

There are `r prettyNum(nrow(warpbreaks) ^3, big.mark = ",")` rows cubed in the warpbreaks dataset.

prettyNum isn't necessary but it adds commas that improve readability.

